---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

knit_print.data.frame = function(x, ...) {
  res = paste(c("", "", knitr::kable(x)), collapse = "\n")
  knitr::asis_output(res)
}
registerS3method(
  "knit_print", "data.frame", knit_print.data.frame,
  envir = asNamespace("knitr")
)
```

# gendered

<!-- badges: start -->
<!-- badges: end -->

The goal of `gendered` is to provide functions that can extract various gendered forms of speech in **German**. Right now it includes the following forms:

1. Gendered pair form (i.e. "Studenten und Studentinnen")
2. Gendered symbol form (i.e. "StudentInnen", "Student:innen", "Student*innen" etc.)
3. Gender neutral form (i.e. "Studierende")

## Installation

You can install the development version of `gendered` from GitHub with:

``` r
# install.packages("remotes)
remotes::install_github("vivifabrien/gendered")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(gendered)
## basic example code
```

## Pair form examples

```{r}
pair_examples <- data.frame(text = c("Liebe Migranten und Migrantinnen, liebe Arbeiterinnen und Arbeiter.", 
                                   "Es ist wichtig sich speziell für Arbeiterinnen einzusetzen.",
                                   "Die Bürger und Bürgerinnen verlangen mehr.",
                                   "Bin beim Treffen ehemaliger Stipendiaten und Stipendiatinnen!",
                                   "Polen und auch Polinnen verdienen zu wenig.",
                                   "Innenministerium des Bundes"),
                              text_id = 1:6) 

pair_examples %>% 
  gendered_pairs(text)
```

## Gendered symbol forms


```{r}
symbol_examples <- data.frame(text = c("Liebe MigrantInnen & ImmigrantInnen.", 
                                   "Es ist wichtig sich speziell für Arbeiterinnen einzusetzen.",
                                   "Die Bürger:innen verlangen mehr.",
                                   "Bin beim Treffen ehemaliger Stipendiaten/innen!",
                                   "Frankfurter/-innen verdienen zu wenig.",
                                   "Innenministerium des Bundes"),
                              text_id = 1:6) 

symbol_examples %>% 
  gendered_symbols(text) 
```

## Gender neutral forms


```{r}
neutral_examples <- data.frame(text = c("Liebe Studierende und Auszubildende.", 
                                   "Es ist wichtig sich für die Arbeitenden einzusetzen.",
                                   "Geflüchtete sind wichtige Mitglieder der Gesellschaft."),
                              text_id = 1:3) 

neutral_forms <- neutral$gendergerechte_alternativen %>%
  paste0("\\b", ., "\\b") %>%
  paste0(collapse = "|")

neutral_examples %>% 
  dplyr::mutate(neutrals = stringr::str_extract_all(text, neutral_forms)) %>%
  tidyr::unnest_longer(neutrals)
```


